The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-07-23 paper2_JNLS/paper.tex
NM

Recall that the abrupt depth change is met by traveling waves at some time $t = T_{ADC}$, and for simplicity we set $T_{ADC} = 0$. The KdV equations govern the evolution and nonlinear dispersion of waves over long timescales (specifically, longer than ???). Meanwhile, wave evolution over shorter timescales is much simpler in that it is simply noninteracting traveling waves with uniform wave speed $c = \sqrt{g \depth}$ (i.e. no nonlinearity and no dispersion). Hence, a short instant after waves pass over the ADC, the waveform does not yet have time to alter significantly, which gives the (deterministic) matching condition
\begin{align}
&u(x,t) \vert_{t=0^-} = u(x,t) \vert_{t=0^+} \qquad \text{for } x \in [-\pi, \pi]
%&&\mbox{\em deterministic matching condition}
\end{align}
%or in Johnson's formulation, it is $\depth^{1/4} \eta$ that matches.

>>>>

Recall that the abrupt depth change is met by traveling waves at some time $t = T_{ADC}$, and for simplicity we set $T_{ADC} = 0$. The KdV equations govern the evolution and nonlinear dispersion of waves over long timescales (specifically, $t \gg \delta^{-2}$ for dimensionless time). Meanwhile, wave evolution over shorter timescales, $t \ll \delta^{-2}$, is much simpler in that it is simply noninteracting traveling waves with uniform wave speed $c = \sqrt{g \depth}$ (i.e. no nonlinearity and no dispersion). Hence, a short instant after waves pass over the ADC, the waveform does not yet have time to alter significantly, which gives the (deterministic) matching condition
\begin{align}
&u(x,t) \vert_{t=0^-} = u(x,t) \vert_{t=0^+} \qquad \text{for } x \in [-\pi, \pi]
%&&\mbox{\em deterministic matching condition}
\end{align}
%or in Johnson's formulation, it is $\depth^{1/4} \eta$ that matches.
